Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-06 draft/paper1_v11.tex
Jenny's comment: 1

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH
% Version 6; MNRAS format; Paper I edited by JG
% Version 7; MNRAS format; Edited by SH

@@

%% ------------------------------------------------------------------------------------ %% 
\title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halo of 
	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam}

@@

\begin{abstract}

    Massive galaxies are important to our understanding of galaxy formation, and 
    their extended stellar halos contain crucial fossil records of their assembly 
    history. 
    In this work, we use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), 
    high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) 
    survey to investigate the surface mass density profiles and outer stellar halos 
    of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    Shallow images and/or over-simplified models like the \texttt{CModel} tend to 
    miss the extended stellar halo and result in underestimated stellar mass in a 
    mass-dependent way.  
    It will impact important applications like the measurements of the stellar mass 
    function. 
    With these deeper data, we explicitly show that at fixed stellar mass,
    massive central galaxies display surface mass density profiles that are not 
    self-similar, with the outer-slope becoming shallower and the fraction of mass 
    in the outskirt increasing with total stellar mass.
    We also show that the ellipticity of the stellar halo increases with stellar
    mass, while the optical color gradients do not strongly depend on stellar mass.
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretions of small systems. 
    The surface mass density profiles are provided in a convenient tabulated format 
    in order to facilitate comparisons with predictions from numerical simulations 
    of galaxy formation.

\end{abstract}

@@

    Massive galaxies are fascinating objects that have experienced complex assembly 
    process and dramatic evolution.  
    They are crucial for both cosmology and the study of galaxy formation. 
    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter 
    halos and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many 
    open questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation 
    scenario (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies 
    (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
    instabilities or gas-rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the 
    population of massive quiescent galaxies at high redshift that have smaller 
    average effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, 
    vanDokkum2008, Cimatti2008}), slightly higher central velocity dispersion and 
    stellar mass density (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), and 
    more disk-like morphologies (e.g. \citealt{vanderWel2011}) than their local 
    descendants (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar 
    mass.

    Following this initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quench star formation in 
    massive galaxies. 
    A large fraction of these massive progenitors became quiescent at $z>1$ 
    (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase of their assembly is driven by non-dissipative processes such 
    as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
    To explain the observed increase of $R_{\mathrm{e}}$ (e.g. 
    \citealt{Newman2012, vdWel2014}) as well as the build-up of the outer stellar 
    halos of ETGs (e.g. \citealt{Szomoru2012, Patel2013}), the ``two-phase'' 
    scenario suggests that minor mergers should dominate the mass assembly during 
    the second phase (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, 
    Laporte2013}).
    Both numerical simulations (e.g. \citealt{Oser2010}) and 
    semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
    mass fraction in the accreted component should increase with total stellar mass, 
    despite their technical differences (e.g. \citealt{Lackner2012, Cooper2013, 
    Qu2017}).
    For instance, recent result from the Illustris \footnote{
    \texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predicts that the fraction of  
    accreted stars increases significantly with total stellar mass at \logms{}$>11.0$, 
    and the accreted component starts to dominate the stellar mass budget 
    ($f_{\mathrm{accreted}}>0.5$) at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
%% ------------------------------------------------------------------------------------ %%

    Given the success of this two-phase scenario in explaining trends like overall size 
    growth, it is time to confront their predictions with additional observations, 
    especially the detailed profiles of surface mass density and shape for low redshift 
    massive galaxies.  
    Early one-dimensional analysis of nearby massive ETGs suggest that the 
    single-\ser{} profile can describe their surface brightness (or surface mass 
    density) profiles reasonably well (e.g. \citealt{Kormendy2009}; except for the
    most central region), with the \ser{} index increasing with total luminosity 
    (e.g. \citealt{Graham2013}).
	However, the situation is in fact more complicated, with a suggestion from 
	\citet{Schombert2015} that there are actually two families of light profiles:
	the ones that follow single-\ser{} law well and the ones show significant 
	deviation.
	Two-dimensional analysis, meanwhile, finds that the stellar distributions 
    of massive ETGs are often better fit by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}). 
    \citet{Huang2013b} further suggests a connection between the multi-component 
    nature of massive galaxies and their two-phase assembly history. 
    To further confront the two-phase scenario requires very deep observations of 
    large samples of massive ETGs to correctly estimate their total stellar mass 
    (e.g. \citealt{Bernardi2013, DSouza2014}) and explore their assembly history via 
    their extended, accreted halos (e.g. \citealt{Capaccioli2015, Iodice2016, 
    Iodice2017}).
    Currently, such work is limited by the depth of imaging from large-area surveys 
    such as the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}) or
    the small sample size of massive galaxies with deep images.

    In this paper, we take advantage of new high-quality (median 
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
    as a function of their properties. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    With the help of reliable spectroscopic and photometric redshift 
    (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
    we select a large sample (${\sim} 7000$) of massive central galaxies at 
    $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer. 
    In this paper, we use this sample to 
    (a) reliably measure individual surface mass density (\mden{}) profile of 
    massive galaxy out to 100 kpc, 
    (b) investigate the dependence of their outer stellar halos on total stellar 
    mass, and 
    (c) examine the implications for the stellar mass function (SMF) when the outer 
    halos of massive galaxies are accounted for.   
    In a second paper in this series, we will further look into the potential 
    environmental dependence of structures in massive ETGs (Huang\etal in prep.).

    This paper is organized as follows. 
    Section \ref{sec:data} presents our data and our sample selection. 
    Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
    brightness profiles. 
    Section \ref{sec:mstar} describes how we estimate stellar mass. 
    Our main results are presented in Section \ref{sec:result} and discussed in 
    Section \ref{sec:discussion}. 
    Section \ref{sec:summary} presents our summary and conclusions.

@@

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the 
    $i$-band surface brightness limit than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 
    0.6\asec) and the wide area, the HSC survey represents a tremendous dataset to 
    perform large statistical study of the surface brightness profiles of massive
    galaxies out to their very outskirts.     
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

	HSC $i$-band images typically have the best seeing compared to other bands because 
	of strict requirements driven by weak lensing science. 
    We will therefore use the $i$-band images to measure the stellar distributions of 
    massive galaxies.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_diff_new}
      \caption{              
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for massive
      	  galaxies (grey dots).
      	  The running-median of the mass differences along with the standard deviations
      	  in a series of mass bins are shown in large red, hexagons with error bars. 
          On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for all galaxies (shaded 
          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
          \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
          The average difference is small (0.02 dex) and does not show 
          clear mass--dependence. 
          }
      \label{fig:mass_diff}
  \end{figure*}

@@

    We begin by using a broad luminosity cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on \citet{Leauthaud2016}, $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag can 
    define a sample that includes almost all \logms{}$\geq 11.5$ galaxies.    
    We therefore made a conservative selection of initial sample of massive galaxies
    with $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences
    between the response curves of SDSS-$i$ and HSC-$i$ filters.}
    and also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in the $i$-band.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

    We further select extended objects with no deblending errors, with well defined 
    centroids, and with useful \texttt{cModel} magnitudes in all five bands. 
    After removing objects that have pixels affected by saturation, cosmic-rays, or 
    other optical artifacts\footnote{each criterion removes less than 8\% of the 
    entire sample.}. This sample corresponds to 1760845 galaxies and will be referred 
    as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

@@

    Objects without a spectroscopic redshift are matched with the central 
    galaxies from the \redm{} catalog using a $2.0^{\arcsec}$ matching radius. 
    We keep the matched objects with useful red-sequence photo-$z$ 
    ($0.3 \leq z_{\lambda} < 0.5$) in the final sample. 
    These galaxies are the best candidates for centrals in clusters selected from 
    SDSS DR8 data (\citealt{SDSSDR8}) via a well-tested red-sequence method. 
    The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
    for the goal of this work.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
    spec-$z$. and the GAMA survey provides additional $14$\% of spec-$z$.
    We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
    (1) The inner region of massive galaxies can be resolved, and \mstar{} within 
    10 kpc can be reliably measured; 
    (2) The background noise and cosmological dimming are not major issues and the 
    \mden{} profile can be measured out to $>100$ kpc; 
    (3) Evolution in structure and stellar population properties can be largely 
    ignored.  
    At both lower and higher redshift, the completeness of spec-$z$ sample starts 
    to decline.  
    Also for bright galaxies at lower redshift, the over-subtraction of background 
    becomes a more serious issue. 
    Before we can define our mass-complete sample of massive galaxies required for 
    our analysis, we describe our one-dimensional photometric analysis 
    (\S \ref{sec:ellipse}) and stellar mass estimations (\S \ref{sec:mstar}). 
    We then define the final sample in \S \ref{sec:final}.

@@

    The surface brightness profile of massive ETG can not be well modeled by the 
    de~Vaucouleurs or single-\ser law, especially at the imaging depth of HSC.
    These models will fail to simultaneously describe the profile in both the inner 
    and the outer regions and also cannot account for any radial variations in 
    ellipticity and position angle. 
    In principle, massive galaxies can still be described by more complex 
    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
    sensitive to the choices of models (e.g. de~Vaucouleurs or \ser{} profile), 
    the number of components, initial guesses of parameters, and the internal 
    degeneracies among different parameters. 
    Background subtraction uncertainty also affects the 2-D model fitting 
    dramatically, especially for massive ETGs in our sample. 
    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
    galaxies and measure their one-dimensional profiles of stellar mass surface 
    density (\mden{}). 
    This 1-D method we adopt is less affected by the issues mentioned above. 
    Also, we will only study galaxies in the radial range where we are not 
    sensitive to either the PSF ($r<3-5$ kpc) or the background subtraction 
    ($r>100$ kpc).

    We prepare large $i$-band cut-outs for each galaxy that extend to 750 kpc in 
    radius, along with a bad pixel mask and the PSF model. 
    These cut-outs include all of the light of the galaxy and are large enough to 
    also evaluate the background level. 
    We choose to use $i$-band images because they trace the stellar distributions of 
    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background levels than the $z$ 
    and $y$ band images (although these in principle may be better tracers of 
    \mden{}).

@@

    For physical (e.g.\ late-stage major merger) and nuisance (e.g.\ nearby foreground 
    galaxy or bright star) reasons, we cannot extract reliable 1-D profiles for a small 
    fraction of massive galaxies because they are heavily masked out. 
    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
    the sample.
    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
    %\nbcg{} sample. 
    It is worth noting that this excludes most major-merging massive galaxies.

    Given our exquisite profiles that extend to 100 kpc, the definition and meaning 
    of ``total'' magnitude (and stellar mass) becomes more nuanced.
    With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
    we integrate the profile to a range of radii, and estimate the stellar mass 
    within these different apertures.  
    Motivated by the two-phase scenario, we will consider two benchmark physical 
    apertures throughout this work:

@@

        \item \textbf{The \mstar{} within the inner 10 kpc} 
            (hereafter noted \minn{}). 
            According to the two-phase scenario, the \textit{in situ} star-formation 
            quickly builds up the inner, dense core of massive ETGs.  
            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
            simulations (e.g. \citealt{RodriguezGomez2016}), the \textit{in situ} 
            component dominates the \mstar{} within one effective radius 
            ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
            We therefore use \minn{} as proxy for the mass forged during the 
            \textit{in situ} phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over 
            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshift 0.3 and 0.5).  
            It is worth noting that, at very high-\mstar{} end, there can be 
            significant contribution of accreted stars within 10 kpc 
            (e.g. \citealt{RodriguezGomez2016}). 
            We will further discuss the justification of this assumption in 
            \ref{ssec:twophase}.

@@

    On the same figure, we also compare the HSC results with the ones from following 
    works:

>>>>

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH
% Version 6; MNRAS format; Paper I edited by JG
% Version 7; MNRAS format; Edited by SH
% Version 10; MNRAS format; Edited by AL and JG
% Version 11; MNRAS format; Edited by SH

@@

%% ------------------------------------------------------------------------------------ %% 
\title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halos of 
	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam}

@@

\begin{abstract} Massive galaxies display extended light profiles that can reach out to several hundreds of kiloparsecs. These extended stellar halos are key fossil records of the assembly history of massive galaxies.  Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in the $i$-band), we  present a systematic study of the stellar halos of the most massive galaxies (\mstar{}$\geq 11.5$) using a statistically significant sample of more than $7000$ galaxies at $0.3 < z < 0.5$. Our  study is based on high-quality (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey which reaches ${\sim}4$ magnitudes fainter than SDSS and  enables us to directly trace mass profiles to 100 kpc without resorting to stacking. Shallow images and/or over-simplified models like \texttt{CModel} cannot capture the extended stellar halo and result in underestimated stellar masses. We show that this has a signifcant impact on  the high mass end of the galaxy mass function. The surface mass density profiles of massive galaxies are not self-similar; at fixed "core mass" they display a diverse  range of outer profiles. Galaxies in our sample have optical color gradients that are independent of galaxy mass but stellar halo ellipticites that increases with galaxy mass. Our results are broadly consistent with the two phase formation scenario of massive galaxies in which outer envelopes are built up at late times from minor merging. We provide surface mass surface mass density profiles in a convenient tabulated format to facilitate comparisons with predictions from numerical simulations of galaxy formation.\end{abstract}

%massive central galaxies display surface mass density profiles that are not 
%    self-similar, with the outer-slope becoming shallower and the fraction of mass 
%    in the outskirt increasing with total stellar mass (xxxxxxxxx).

@@

    Simulations of structure formation within the context of the $\Lambda$-CDM 
    cosmological model make predictions for the hierarchical growth of dark matter 
    halos and galaxies (e.g. \citealt{Baugh1996, DeLucia2006}), but there are many 
    open questions regarding the star-formation history, mass assembly process, and 
    structural evolution of massive galaxies. 
    Massive galaxies are thought to grow according to a ``two-phase'' formation 
    scenario (e.g. \citealt{Oser2010, Oser2012}). 
    In this scenario, the progenitors of $z{\sim} 0$ massive early-type galaxies 
    (ETGs) undergo a rapid growth phase at $z{\sim} 2$ triggered either by disk 
    instabilities or gas-rich mergers (e.g. \citealt{Hopkins2008, Dekel2009}). 
    Observationally, the progenitors of ETGs are thought to correspond to the 
    population of massive quiescent galaxies at high redshift that have smaller 
    average effective radii ($R_{\mathrm{e}}$; e.g. \citealt{Trujillo2006, 
    vanDokkum2008, Cimatti2008}).  These high redshift galaxies also have slightly higher central velocity dispersions and stellar mass densities (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), and 
    more disk-like morphologies (e.g. \citealt{vanderWel2011}) than low redshift galaxies (e.g. \citealt{Bezanson2009, vanDokkum2010}) with similar stellar 
    mass.

    Following this initial epoch of early formation, feedback from stars and/or AGN 
    (e.g. \citealt{Sijacki2007, Fabian2012}) efficiently quenches star formation in 
    massive galaxies. 
    A large fraction of these massive progenitors are already quiescent by $z=1$ 
    (e.g. \citealt{Bezanson2009, Kriek2016}). 
    The second phase of their assembly is driven by non-dissipative processes such 
    as dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). The ``two-phase'' formation of massive galaxies is  designed to both explain the observed increase in the effective radii ($R_{\mathrm{e}}$) of massive galaxies (e.g. 
    \citealt{Newman2012, vdWel2014}) and the build-up of stellar 
    halos  (e.g. \citealt{Szomoru2012, Patel2013}). According to this formation mecanisms, minor mergers dominate the mass assembly of massive galaxies at late times (e.g. \citealt{Hilz2012, Hilz2013, Oogi2013, Bedorf2013, Laporte2013}).

    Both numerical simulations (e.g. \citealt{Oser2010}) and 
    semi-analytic models (SAM; e.g. \citealt{LeeYi2013, LeeYi2017}) agree that the 
    mass fraction in the accreted component should increase with total galaxy stellar mass (e.g. \citealt{Lackner2012, Cooper2013, 
    Qu2017}). For instance, recent results from the Illustris \footnote{
    \texttt{http://www.illustris-project.org/}} simulation 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) predicts that the fraction of  
    accreted stars increases significantly and reaches $f_{\mathrm{accreted}}>0.5$ at \logms{}$>11.5$ (\citealt{RodriguezGomez2016}).
%% ------------------------------------------------------------------------------------ %%

    Given the success of this two-phase scenario in explaining trends like overall size 
    growth, it is time to confront this model with additional observations,  in particular, the detailed surface mass density profiles of low redshift massive galaxies. Early studies based on one-dimenstional light profiles, suggested that the profiles of nearby ETGs are well described by single-\ser{} profiles (e.g. \citealt{Kormendy2009}; except for the
    most central region) and that the \ser{} index increases with total luminosity 
    (e.g. \citealt{Graham2013}). However,  later work revealed a more complicated  situation  showing  that  ETGs  belong to two famillies, those that follow single-\ser{} law, versus those that significant deviation from the single-\ser{} profile \citep{Schombert2015}. Two-dimensional analyses have found that the stellar distributions of massive ETGs are often better fit by multiple-component models 
    (e.g. \citealt{Huang2013a, Oh2017}).  \citet{Huang2013b} further suggest a connection between the multi-component 
    nature of massive galaxies and their two-phase assembly history. 
    To further confront the two-phase scenario requires very deep observations of 
    large samples of massive ETGs to correctly estimate their total stellar masses
    (e.g. \citealt{Bernardi2013, DSouza2014}) as well as to quantify the amplitude and scatter among outer enveloppes (e.g. \citealt{Capaccioli2015, Iodice2016, 
    Iodice2017}).

    To-date,  studies of the profiles of massive galaxies have been  either  been conducted  using large samples but with shallow imaging, for example the Sloan Digital Sky Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}), or with deeper imaging  but smaller samples sizes (e.g cite CLASH AND FRONTIER FIELDS??). In this paper, we take advantage of new high-quality (median  seeing of
    FWHM${\sim} 0.6^{\arcsec}$ in the $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) images from the Hyper Suprime-Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the light profiles of massive galaxies out to 100 kpc. The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. We select a large sample (${\sim} 7000$) of massive central galaxies at $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.

 %       With the help of reliable spectroscopic and photometric redshift 
 %   (e.g. the ones for \redm{} clusters, \citealt{Rykoff2014}; \citealt{Rozo2015b}),
 %   we select a large sample (${\sim} 7000$) of massive central galaxies at 
 %   $0.3 < z < 0.5$ using ${\sim} 100$ deg$^2$ of data from the HSC wide layer.

    In this paper, we use this sample to 
    (a) reliably measure individual surface mass density (\mden{}) profiles of 
    massive galaxy out to 100 kpc, 
    (b) investigate the dependence of their outer stellar halos on total stellar 
    mass, and 
    (c) examine the implications in terms of  evaluating the high mass end of the galaxy stellar mass function (SMF). In a second paper in this series, we will investigate the environmental (dark matter halo mass) dependence of the sizes of massive ETGs (Huang\etal in prep.).

    This paper is organized as follows. 
    Section \ref{sec:data} presents our data and sample selection. 
    Section \ref{sec:ellipse} describes our procedure for extracting 1-D surface 
    brightness profiles. 
    Section \ref{sec:mstar} describes how we estimate stellar mass. 
    Our main results are presented in Section \ref{sec:result} and discussed in 
    Section \ref{sec:discussion}. 
    Section \ref{sec:summary} presents our summary and conclusions.

@@

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in terms of the $i$-band surface brightness limit than SDSS. Combined with the excellent imaging resolution (the median $i$-band seeing is 
    0.6\asec) and the wide area, the HSC survey represents a tremendous dataset to 
    perform large statistical studies of the surface brightness profiles of massive
    galaxies out to their very outskirts.     
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

	HSC $i$-band images typically have the best seeing compared to other bands because 
	of strict requirements driven by weak lensing science. 
    We will therefore use $i$-band images to measure the stellar distributions of 
    massive galaxies.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_diff_new}
      \caption{              
          \textbf{Left:} Difference between \mcmodel{} and \mtot{} for massive
      	  galaxies (grey dots).
      	  The running-median of the mass difference is shown by large red hexagons. On average, \mcmodel{} underestimates the total stellar mass of massive 
          galaxies by 0.1 dex while in some cases, the difference can exceed 0.2 dex.
          Vertical histograms indicate the mass difference for all galaxies (shaded 
          histogram) and for the ones with \logmtot{}$>11.6$ (empty histogram).
          \textbf{Right:} Difference between \mmax{} and \mtot{} in the same format. 
          The average difference is small (0.02 dex) and with no clear mass--dependence. }
      \label{fig:mass_diff}
  \end{figure*}

@@

    We begin by using a broad luminosity cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on \citet{Leauthaud2016}, $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag can 
    define a sample that includes almost all \logms{}$\geq 11.5$ galaxies.    
    We therefore perform an initial conservative selection of massive galaxies
    with $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect small differences
    between the response curves of the SDSS-$i$ and HSC-$i$ filters.}. We also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in the $i$-band.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

    We further select extended objects with no deblending errors, with well defined 
    centroids, and with useful \texttt{cModel} magnitudes in all five bands. 
    After removing objects that have pixels affected by saturation, cosmic-rays, or 
    other optical artifacts\footnote{each criterion removes less than 8\% of the 
    entire sample.}, this sample corresponds to 1760845 galaxies and will be referred 
    as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

@@

    Objects without a spectroscopic redshift are matched with central 
    galaxies from the \redm{} SDSS DR8 (\citealt{SDSSDR8}) catalog using a $2.0^{\arcsec}$ matching radius. Matched objects with a red-sequence photo-$z$ ($0.3 \leq z_{\lambda} < 0.5$) are included in our sample. The accuracy of the red-sequence photo-$z$ is sufficient (median 
    $|z_{\lambda} - z_{\mathrm{Spec}}| {\sim} 0.01$ for the ones with spec-$z$) 
    for the goal of this work.
    The \redm{} catalog provides an additional 133 unique redshifts for massive 
    galaxies in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"

    In total, at $0.3 \leq z \leq 0.5$, our sample consists of 25286 galaxies with 
    reliable redshift information (referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    The majority of our redshifts come from the BOSS and SDSS ``legacy'' LRG samples. The GAMA survey provides an additional $14$\% of spec-$z$.
    We choose the redshift range of $0.3 \leq z \leq 0.5$ to make sure that 
    (1) The inner region of massive galaxies can be resolved, and \mstar{} within 
    10 kpc can be reliably measured; 
    (2) The background noise and cosmological dimming are not major issues and the 
    \mden{} profile can be measured out to $>100$ kpc; 
    (3) Redshift evolution in the stellar population properties can be largely 
    ignored.  
    Also at higher redshift, the completeness of the spec-$z$ sample starts to decline. And finally, the over-subtraction of the background level becomes a more serious issue at lower redshifts.  We will now describe our one-dimensional photometric analysis  (\S \ref{sec:ellipse}) and our stellar mass estimates (\S \ref{sec:mstar}). We will then define the final sample in \S \ref{sec:final}.

@@

    The surface brightness profiles of massive ETG are not well modeled by the 
    de~Vaucouleurs or single-\ser law, especially at the imaging depth of HSC.
    These models will fail to simultaneously describe the profile in both the inner 
    and the outer regions and also cannot account for any radial variations in 
    ellipticity and position angle. 
    In principle, massive galaxies can still be described by more complex 
    models (e.g \citealt{Huang2013a, Huang2013b, Oh2017}), but they are still 
    sensitive to the choice of a particular model (e.g. de~Vaucouleurs or \ser{} profile), 
    the number of components, initial guesses of parameters, and internal 
    degeneracies among different parameters. 
    Background subtraction uncertainties can also affect the 2-D model fitting method, especially for the massive ETGs that make up our sample.

    We therefore perform elliptical isophote fitting using the IRAF \texttt{Ellipse} 
    algorithm (Jedrzejewski 1987) to estimate the total luminosities of massive 
    galaxies and to measure their one-dimensional stellar mass surface 
    density profiles (\mden{}). 
    This 1-D method is less affected by the issues mentioned above. 
    Also, we will only study galaxies in the radial range where we are not 
    sensitive to either the PSF ($r<3-5$ kpc) or the background subtraction 
    ($r>100$ kpc).

    We prepare large $i$-band postage-stamkps for each galaxy that extend to 750 kpc in 
    radius, along with a bad pixel mask and the PSF model. 
    These postage-stamlps include all of the light of the galaxy and are large enough to 
    also evaluate the background level. 
    We choose to use $i$-band images because they trace the stellar distributions of 
    massive galaxies at $0.3 \leq z \leq 0.5$ reasonably well 
    (the observed i-band corresponds to a rest-frame $g$ or $r$ band), but also 
    because they have better seeing and much lower background levels than the $z$ 
    and $y$ band images (although these in principle may be better tracers of 
    \mden{}).

@@

    For physical (e.g.\ late-stage major merger) and nuisance (e.g.\ nearby foreground 
    galaxy or bright star) reasons, we cannot extract reliable 1-D profiles for a small 
    fraction of massive galaxies because they are heavily masked out. 
    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
    the sample.
    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
    %\nbcg{} sample. 
    It is worth noting that this excludes most massive galaxies undergoing major mergers.

    Given our exquisite profiles that extend to 100 kpc, the definition and meaning 
    of ``total'' magnitude (and stellar mass) becomes nuanced.
    With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
    we integrate the profile to a range of radii, and estimate the stellar mass 
    within these different apertures.  
    Motivated by the two-phase scenario, we will consider two benchmark physical 
    apertures throughout this work:

@@

        \item \textbf{The \mstar{} within the inner 10 kpc} 
            (hereafter noted \minn{}). 
            According to the two-phase scenario, the \textit{in situ} star-formation phase quickly builds up the inner, dense core of massive ETGs.  
            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
            simulations (e.g. \citealt{RodriguezGomez2016}), the \textit{in situ} 
            component dominates the \mstar{} within one effective radius 
            ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
            We therefore use \minn{} as proxy for the mass forged during the 
            \textit{in situ} phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over 
            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshifts 0.3 and 0.5 respectively).  
            It is worth noting that, at the very high-\mstar{} end, accreted stars may make a significant contribution to the mass within 10 kpc 
            (e.g. \citealt{RodriguezGomez2016}). We will further discuss the justification of this assumption in 
            \ref{ssec:twophase}.

@@

    In Figure \ref{fig:smf} we also compare our results  with the following previous studies:
